---
title: "RAINFOR Woody Biomass and GEOSCHEM NBE data summary"
output:
  html_document:
    css: styles.css
    df_print: paged
---
<style type="text/css">
.main-container {
  max-width: 2500px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```{r echo = FALSE, message=FALSE, warning=FALSE}
library(ncdf4); library(raster); library(dplyr);library(ggplot2);library(ggpubr);library(quantreg);library(ggpp);library(rgeos);library(ggpmisc);library(rgdal);library(Metrics);library(kableExtra)

```

Summary of raw RAINFOR biomass data as sent by Leeds after analysis. Plots of Above ground woody biomass in t/ha and woody productivity and mortalityt/ha/yr
```{r echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 8}
options(width = 100)

#amazon subset
amazonia_subset <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazonia_subset.shp")
#amazon ecoregions
amazon_nw_poly <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazon_nw.shp");amazon_sw_poly <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazon_sw.shp");amazon_ec_poly <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazon_ec.shp");amazon_bs_poly <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazon_bs.shp");amazon_gs_poly <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazon_gs.shp")

#wood productivity t/ha/year
woodprod_00_09 <- brick('R://brazil_leeds_maps/WoodyProductivity20002009_Mg_perHa_perYear_111km.tif')
woodprod_10_16 <- brick('R://brazil_leeds_maps/WoodyProductivity20102016_Mg_perHa_perYear_111km.tif')
#biomass mortality t/ha/year
biommort_00_09 <- brick('R://brazil_leeds_maps/BiomassMortality_20002009_Mg_perHa_perYear_111km.tif')
biommort_10_16 <- brick('R://brazil_leeds_maps/BiomassMortality_20102016_Mg_perHa_perYear_111km.tif')
#biomass t/ha
biomass_amazon <- brick('R://brazil_leeds_maps/AbovegroundBiomass_Mg_perHa_111km.tif')

# #plots
# plot(biomass_amazon,main='Woody Biomass t/ha')
# plot(woodprod_00_09,main='Woody Productivity 2000-2009 t/ha/year')
# plot(woodprod_10_16,main='Woody Productivity 2010-2016 t/ha/year')
# plot(biommort_00_09,main='Woody Mortality 2000-2009 t/ha/year')
# plot(biommort_10_16,main='Woody Mortality 2010-2016 t/ha/year')


# fmet<-c('','Mean','SD')
# fwb<-c('Woody Biomass',formatC(cellStats(biomass_amazon, 'mean'), format="f", big.mark=",", digits=0),formatC(cellStats(biomass_amazon, 'sd'), format="f", big.mark=",", digits=0))
# fwp1<-c('Woody Productivity 2000-2009',formatC(cellStats(woodprod_00_09, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(woodprod_00_09, 'sd'), format="f", digits=2))
# fwp2<-c('Woody Productivity 2010-2016',formatC(cellStats(woodprod_10_16, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(woodprod_10_16, 'sd'), format="f", digits=2))
# fwm1<-c('Woody Mortality 2000-2009',formatC(cellStats(biommort_00_09, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(biommort_00_09, 'sd'), format="f", digits=2))
# fwm2<-c('Woody Mortality 2010-2016',formatC(cellStats(biommort_10_16, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(biommort_10_16, 'sd'), format="f", digits=2))
# as.data.frame(bind_cols(fmet,fwb,fwp1,fwp2,fwm1,fwm2))


```

Mean and Std Dev. RAINFOR data after including BGB and converted to g.m-2 and g.m-2.d-1 
```{r echo = FALSE, message=FALSE}
options(width = 100)
#functions for modification
thayr_to_gCm2day_fun <- function(x) {
  x *0.48 * (100/365.25) }
tha_to_gCm2_fun <- function(x) {
  x *0.48 * 100 }
bgb_inclusion <- function(x){
  x+(0.489 * x ** 0.89)
}

#include BGB to wood dynamics
woodprod_00_09 <- calc (woodprod_00_09,bgb_inclusion)
woodprod_10_16 <- calc (woodprod_10_16,bgb_inclusion)
biommort_00_09 <- calc (biommort_00_09,bgb_inclusion)
biommort_10_16 <- calc (biommort_10_16,bgb_inclusion)
biomass_amazon <- calc (biomass_amazon,bgb_inclusion)

#convert to gcm2
woodprod_00_09_gCm2d <- calc(woodprod_00_09, thayr_to_gCm2day_fun)
woodprod_10_16_gCm2d <- calc(woodprod_10_16, thayr_to_gCm2day_fun)
biommort_00_09_gCm2d <- calc(biommort_00_09, thayr_to_gCm2day_fun)
biommort_10_16_gCm2d <- calc(biommort_10_16, thayr_to_gCm2day_fun)
biomass_amazon_gCm2 <- calc(biomass_amazon, tha_to_gCm2_fun)

rt_amazon_00_09_day<-biomass_amazon_gCm2/biommort_00_09_gCm2d
rt_amazon_00_09_year<-rt_amazon_00_09_day/365.25
rt_amazon_10_16_day<-biomass_amazon_gCm2/biommort_10_16_gCm2d
rt_amazon_10_16_year<-rt_amazon_10_16_day/365.25

met<-c('','Mean','SD')
wb<-c('Woody Biomass',formatC(cellStats(biomass_amazon_gCm2, 'mean'), format="f", big.mark=",", digits=0),formatC(cellStats(biomass_amazon_gCm2, 'sd'), format="f", big.mark=",", digits=0))
wp1<-c('Woody Productivity 2000-2009',formatC(cellStats(woodprod_00_09_gCm2d, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(woodprod_00_09_gCm2d, 'sd'), format="f", digits=2))
wp2<-c('Woody Productivity 2010-2016',formatC(cellStats(woodprod_10_16_gCm2d, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(woodprod_10_16_gCm2d, 'sd'), format="f", digits=2))
wm1<-c('Woody Mortality 2000-2009',formatC(cellStats(biommort_00_09_gCm2d, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(biommort_00_09_gCm2d, 'sd'), format="f", digits=2))
wm2<-c('Woody Mortality 2010-2016',formatC(cellStats(biommort_10_16_gCm2d, 'mean'), format="f", big.mark=",", digits=2),formatC(cellStats(biommort_10_16_gCm2d, 'sd'), format="f", digits=2))

as.data.frame(bind_cols(met,wb,wp1,wp2,wm1,wm2))
```

Visualize histogram and plots
```{r echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 10}
par(mfrow = c(1, 2))
hist(biomass_amazon_gCm2,main='Spread of Woody Biomass gC/m2');plot(biomass_amazon_gCm2,main='Woody Biomass gC/m2');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)

hist(woodprod_00_09_gCm2d,main='Spread of Woody Productivity 2000-2009 gC/m2/day');plot(woodprod_00_09_gCm2d,main='Woody Productivity 2000-2009 gC/m2/day');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)
hist(woodprod_10_16_gCm2d,main='Spread of Woody Productivity 2010-2016 gC/m2/day');plot(woodprod_10_16_gCm2d,main='Woody Productivity 2010-2016 gC/m2/day');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)
hist(biommort_00_09_gCm2d,main='Spread of Woody Mortality 2000-2009 gC/m2/day');plot(biommort_00_09_gCm2d,main='Woody Mortality 2000-2009 gC/m2/day');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)
hist(biommort_10_16_gCm2d,main='Spread of Woody Mortality 2010-2016 gC/m2/day');plot(biommort_10_16_gCm2d,main='Woody Mortality 2010-2016 gC/m2/day');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)
hist(biommort_00_09_gCm2d,main='Spread of Woody Residence time 2000-2009 years');plot(rt_amazon_00_09_year,main='Woody Residence Time 2000-2009 years');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)
hist(rt_amazon_10_16_year,main='Spread of Woody Residence time 2010-2016 years');plot(rt_amazon_10_16_year,main='Woody Residence Time 2010-2016 years');plot(amazon_nw_poly,add=T);plot(amazon_sw_poly,add=T);plot(amazon_ec_poly,add=T);plot(amazon_bs_poly,add=T);plot(amazon_gs_poly,add=T);plot(amazonia_subset,add=T)

```

Calculate uncertainty 
```{r fig.asp = 0.9, fig.width = 10}
#uncertainty calculation
biomass_amazon_gCm2_unc <- biomass_amazon_gCm2*0.25
woodprod_00_09_gCm2d_unc <- woodprod_00_09_gCm2d*0.25
woodprod_10_16_gCm2d_unc <- woodprod_10_16_gCm2d*0.25
biommort_00_09_gCm2d_unc <- biommort_00_09_gCm2d*0.25
biommort_10_16_gCm2d_unc <- biommort_10_16_gCm2d*0.25

cellStats(biomass_amazon_gCm2_unc, 'mean')
cellStats(woodprod_00_09_gCm2d_unc, 'mean')
cellStats(woodprod_10_16_gCm2d_unc, 'mean')
cellStats(biommort_00_09_gCm2d_unc, 'mean')
cellStats(biommort_10_16_gCm2d_unc, 'mean')

lower_biomass_amazon_gCm2 <- biomass_amazon_gCm2-biomass_amazon_gCm2_unc
upper_biomass_amazon_gCm2 <- biomass_amazon_gCm2+biomass_amazon_gCm2_unc

lower_woodprod_00_09_gCm2d <- woodprod_00_09_gCm2d-woodprod_00_09_gCm2d_unc
upper_woodprod_00_09_gCm2d <- woodprod_00_09_gCm2d+woodprod_00_09_gCm2d_unc
lower_woodprod_10_16_gCm2d <- woodprod_10_16_gCm2d-woodprod_10_16_gCm2d_unc
upper_woodprod_10_16_gCm2d <- woodprod_10_16_gCm2d+woodprod_10_16_gCm2d_unc

lower_biommort_00_09_gCm2d <- biommort_00_09_gCm2d-biommort_00_09_gCm2d_unc
upper_biommort_00_09_gCm2d <- biommort_00_09_gCm2d+biommort_00_09_gCm2d_unc
lower_biommort_10_16_gCm2d <- biommort_10_16_gCm2d-biommort_10_16_gCm2d_unc
upper_biommort_10_16_gCm2d <- biommort_10_16_gCm2d+biommort_10_16_gCm2d_unc


```

Compare CARDAMOM data with RAINFOR 
```{r echo = FALSE, message=FALSE, fig.asp = 0.9, fig.width = 10}
load("R:/cssp_brazil/cssp_brazil_R/data/extracted_card.RData")

woody_var<-c('Biomass','Woody NPP 2000/1-2009','Woody NPP 2010-2016','Woody Mortality 2000/1-2009','Woody Mortality 2010-2016')

rainfor_dat <- c(formatC(cellStats(biomass_amazon_gCm2, 'mean'), format="f", big.mark=",", digits=0),
formatC(cellStats(woodprod_00_09_gCm2d, 'mean'), format="f", big.mark=",", digits=2),
formatC(cellStats(woodprod_10_16_gCm2d, 'mean'), format="f", big.mark=",", digits=2),
formatC(cellStats(biommort_00_09_gCm2d, 'mean'), format="f", big.mark=",", digits=2),
formatC(cellStats(biommort_10_16_gCm2d, 'mean'), format="f", big.mark=",", digits=2)
)

rainfor_dat_min <- c(formatC(cellStats(lower_biomass_amazon_gCm2,'mean'), format="f", big.mark=",", digits=0),
                     formatC(cellStats(lower_woodprod_00_09_gCm2d,'mean'), format="f", big.mark=",", digits=2),
                     formatC(cellStats(lower_woodprod_10_16_gCm2d,'mean'), format="f", big.mark=",", digits=2),
                     formatC(cellStats(lower_biommort_00_09_gCm2d,'mean'), format="f", big.mark=",", digits=2),
                     formatC(cellStats(lower_biommort_10_16_gCm2d,'mean'), format="f", big.mark=",", digits=2)
                     )

card_norainfor <- c(formatC(cellStats(cardamom_cwood_0110_mean,'mean'), format="f", big.mark=",", digits=0),
                    formatC(cellStats(cardamom_nppwood_0109_mean,'mean'), format="f", digits=2),
                    formatC(cellStats(cardamom_nppwood_1016_mean,'mean'), format="f", digits=2),
                    formatC(cellStats(cardamom_outputwood_0109_mean,'mean'), format="f", digits=2),
                    formatC(cellStats(cardamom_outputwood_1016_mean,'mean'), format="f", digits=2)
                    )

card_rainfor <- c(formatC(cellStats(cardamom_updated_rainfor_cwood_0110_mean,'mean'), format="f", big.mark=",", digits=0),
                  formatC(cellStats(cardamom_updated_rainfor_nppwood_0110_mean,'mean'), format="f", digits=2),
                  formatC(cellStats(cardamom_updated_rainfor_nppwood_1016_mean,'mean'), format="f", digits=2),
                  formatC(cellStats(cardamom_updated_rainfor_outputwood_0110_mean,'mean'), format="f", digits=2),
                  formatC(cellStats(cardamom_updated_rainfor_outputwood_1016_mean,'mean'), format="f", digits=2)
                  )

rainfor_dat_max <- c(formatC(cellStats(upper_biomass_amazon_gCm2,'mean'), format="f", big.mark=",", digits=0),
                     formatC(cellStats(upper_woodprod_00_09_gCm2d,'mean'), format="f", big.mark=",", digits=2),
                     formatC(cellStats(upper_woodprod_10_16_gCm2d,'mean'), format="f", big.mark=",", digits=2),
                     formatC(cellStats(upper_biommort_00_09_gCm2d,'mean'), format="f", big.mark=",", digits=2),
                     formatC(cellStats(upper_biommort_10_16_gCm2d,'mean'), format="f", big.mark=",", digits=2)
                     )

compare_rainfor_card_mean <- data.frame(woody_var,rainfor_dat,rainfor_dat_min,card_norainfor, card_rainfor,rainfor_dat_max)
compare_rainfor_card_mean
```

Pixel-subset based analysis of assimilated RAINFOR data and GEOSCHEM NBE into CARDAMOM DALEC
```{r echo = FALSE, message=FALSE, fig.asp = 0.5, fig.width = 25}
prefix <- 'R://ILAMB_beta_devel/RAINFOR_leeds_run/cssp_brazil_amazon_run/DATA/benchmark/Amazon_subset_'
suffix <- '_2000_updated_2019.nc'

prefix_new <- 'M://CARDAMOM/CARDAMOM/CARDAMOM_OUTPUTS/DALEC_CDEA_ACM2_BUCKET_MHMCMC/'
midfix <- '_subset/RESULTS_PROCESSED/'
suffix_new <- '_subset_stock_flux.RData'

source('R:/cssp_brazil/cssp_brazil_R/code/subset_pixel_functions_only.R') #imports plotting codes

amazonia_subset <- shapefile("R:/cssp_brazil/cssp_brazil_R/data/amazonia_subset.shp")
compare_var_names <- c('WOOD','NPP_wood_flx','OUTPUT_wood_flx','MTT_wood')
mod_var <- c('esa_cci_biomass_only','esa_cci_agb_nbe',
             'biomass_2010','biomass_initial','biomass_annual',
             'mortality_only','productivity_only',
             'biomass_2010_productivity','biomass_2010_mortality',
             'biomass_initial_productivity','biomass_annual_productivity','biomass_annual_productivity_nbe',
             'biomass_initial_mortality','biomass_annual_mortality',
             'productivity_mortality_only',
             'biomass_2010_productivity_mortality','biomass_initial_productivity_mortality','biomass_annual_productivity_mortality'
             )
time_period <- c('2000-2009','2010-2016')
reference_data<- c(biomass_amazon_gCm2,woodprod_00_09_gCm2d,woodprod_10_16_gCm2d,biommort_00_09_gCm2d,biommort_10_16_gCm2d,rt_amazon_00_09_year,rt_amazon_10_16_year)

par(mfrow = c(3,6))
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[1],mod_var,reference_data,time_period[1])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[1],mod_var,reference_data,time_period[2])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[2],mod_var,reference_data,time_period[1])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[2],mod_var,reference_data,time_period[2])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[3],mod_var,reference_data,time_period[1])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[3],mod_var,reference_data,time_period[2])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[4],mod_var,reference_data,time_period[1])
par(mfrow = c(3,6));one_function_to_plot_them_all(amazonia_subset,compare_var_names[4],mod_var,reference_data,time_period[2])

```

Pixel based analysis of assimilted Rainfor data into CARDAMOM DALEC
```{r echo = FALSE, message=FALSE, fig.asp = 0.9, fig.width = 20}
#load("R:/cssp_brazil/cssp_brazil_R/data/extracted_card.RData")
#source('R:/cssp_brazil/cssp_brazil_R/code/extract_resample_plot.R') #imports plotting codes
# source('R:/cssp_brazil/cssp_brazil_R/code/subset_pixel_functions.R') #imports plotting codes

mod_var_new <- c('esa_cci_agb_only','esa_cci_agb_nbe',
                 'Rainfor_woody_biomass_2010','Rainfor_woody_biomass_initial','Rainfor_woody_biomass_annual',
                 'Rainfor_woody_mortality_only','Rainfor_woody_productivity_only',
                 'Rainfor_woody_biomass_2010_productivity','Rainfor_woody_biomass_2010_and_mortality',
                 'Rainfor_woody_biomass_initial_productivity','Rainfor_woody_biomass_annual_productivity','Rainfor_woody_biomass_annual_productivity_nbe',
                 'Rainfor_woody_biomass_initial_mortality','Rainfor_woody_biomass_annual_mortality',
                 'Rainfor_woody_productivity_and_mortality_only','Rainfor_woody_biomass_2010_productivity_mortality',
                 'Rainfor_woody_biomass_initial_productivity_mortality','Rainfor_woody_biomass_annual_productivity_mortality'
)
mod_var_abr <- c('ECB','ECB_N','B_2010','B_i','B_a','M','P','B_2010_P','B_2010_M',
                 'B_i_P','B_a_P','B_a_P_N','B_i_M','B_a_M','P_M','B_2010_P_M','B_i_P_M','B_a_P_M')
par_names <- c('Lit2SOM (day_1)','GPP%Ra','NPP_fol_frac','NPP_root_frac','Leaf lifespan','TO Wood','TO Roots','Mineralise Lit','SOM2Rh',
               'Temp fac','Canopy Eff (gC/m2leaf/day)','Max bud burst day','NPP_lab_frac','Labile_release_period','max leaf fall',
               'leaf fall period','LMA (gC/m2)','Labile_initial','Foliar_initial','Roots_initial','Wood_initial','Lit_initial',
               'SOM_initial','Soil Water_initial','Cwood_coarseR_frac','CoarseR Biomass 50% Max Depth','Max Root Depth',
               'Res factor Burned Cstocks','CCF Fol','CCF Wood and FineR','CCF Soil','CCF Fol and FineR Lit','unknown','model_var')

param_names <- c('model_var','Lit2SOM (day_1)','GPP%Ra','NPP_fol_frac','NPP_root_frac','Leaf lifespan','TO Wood','TO Roots','Mineralise Lit','SOM2Rh',
               'Temp fac','Canopy Eff (gC/m2leaf/day)','Max bud burst day','NPP_lab_frac','Labile_release_period','max leaf fall',
               'leaf fall period','LMA (gC/m2)','Labile_initial','Foliar_initial','Roots_initial','Wood_initial','Lit_initial',
               'SOM_initial','Soil Water_initial','Cwood_coarseR_frac','CoarseR Biomass 50% Max Depth','Max Root Depth',
               'Res factor Burned Cstocks','CCF Fol','CCF Wood and FineR','CCF Soil','CCF Fol and FineR Lit')

# model_pars_list <- list()
model_pars_df<-as.data.frame(t(data.frame(extract_parameters_all_models(mod_var_new,mod_var_abr))), stringsAsFactors = FALSE)
model_pars_df[] <- lapply(model_pars_df, type.convert, as.is = TRUE)
rownames(model_pars_df)<-  seq_along(model_pars_df[,1])
colnames(model_pars_df)<-  par_names
model_pars_df$model_var<-as.factor(model_pars_df$model_var)
model_pars_df<-model_pars_df[,c(34,1:32)]
model_pars_df$NPP_wood_frac<-1-(model_pars_df[,4]+model_pars_df[,5])
model_pars_df$rt_wood<-1/model_pars_df[,7]
model_pars_df$rt_roots<-1/model_pars_df[,8]
new_model_pars_df<-round_df(model_pars_df[,c(3,34,4,5,14,26,22,20,19,21,23,24,35,36)], 3)
rownames(new_model_pars_df)<-mod_var_abr
kable(new_model_pars_df) %>%
  kable_styling("striped", full_width = F) %>%
  scroll_box(width = "100%", height = "750px")
```
